Group A

### 2021-06-24 group-a/group-a-analysis.Rmd
syncing a variety of changes

```{r message=FALSE, warning=FALSE}
library(dplyr)
library(tidyr)
library(jsonlite)
library(ggplot2)
library(readr)
library(afex)
```

@@

@@

@@

```{r}
hist(prop.in.roi.by.subject$prop.of.samples.in.roi, breaks=20)
```
Exclude subjects below a threshold?

```{r}
bad.subjects <- prop.in.roi.by.subject %>%
  filter(prop.of.samples.in.roi == 0) %>%
  pull(subject_id)

# to match laila's analysis
bad.subjects <- c("5f3a76043bb11c6786e731bf", "5f9c6b2def8bdf1102de5338", "607197e359bae0449ac9d4bc", "60142d5718e5943b09fd9298")

@@

```{r}
first.fixation.after.verb.onset.analysis.data %>%
  group_by(verb_type, subject_id) %>%
  summarize(M=mean(relative.t)) %>%
  ggplot(aes(x=verb_type, y=M, group=subject_id)) +
  geom_point()+
  geom_line()
```

>>>>

```{r message=FALSE, warning=FALSE}
library(dplyr)
library(tidyr)
library(jsonlite)
library(ggplot2)
library(readr)
library(afex)
library(forcats)
```

@@

Mutate value types as needed

```{r}
all.data <- all.data %>%
  mutate(subject_id = factor(subject_id))
```

@@

# Subject Exclusion Criteria

We'll try this two ways. First if we adopt minimal exclusion criteria, removing subjects whose eye tracking data is essentially unusable. Second if we adopt aggressive exclusion criteria, removing subjects with obviously worse eye tracking data.

Set which mode here:
```{r}
# 'AGGRESSIVE' or 'MINIMAL'
exclusion.mode <- 'MINIMAL' 
```

## Proportion of measured data in an ROI.

@@

```{r}
hist(prop.in.roi.by.subject$prop.of.samples.in.roi, breaks=20)
```
Exclude subjects below a threshold

```{r}
if(exclusion.mode == 'AGGRESSIVE') {
  prop.samples.threshold <- 0.2
}
if(exclusion.mode == 'MINIMAL') {
  prop.samples.threshold <- 0
}

bad.subjects.prop.samples <- prop.in.roi.by.subject %>%
  filter(prop.of.samples.in.roi <= prop.samples.threshold) %>%
  pull(subject_id)
```

## Validation accuracy

```{r}
validation.accuracy.data <- all.data %>%
  filter(trial_type == 'webgazer-validate')
```

What % of subjects needed to recalibrate because of poor initial calibration?

```{r}
validation.accuracy.data %>% 
  group_by(subject_id) %>%
  count() %>%
  group_by(n) %>%
  count()
```

Get final average distance for each subject

```{r}
validation.percent <- validation.accuracy.data %>%
  group_by(subject_id) %>%
  slice_tail() %>%
  select(subject_id, percent_in_roi) %>%
  unnest(percent_in_roi) %>%
  group_by(subject_id) %>%
  summarise(M = mean(percent_in_roi), MAX = max(percent_in_roi), MIN = min(percent_in_roi)) %>%
  mutate(subject_id = fct_reorder(subject_id, M))
```

```{r}
ggplot(validation.percent, aes(x=subject_id, y=M, ymax = MAX, ymin=MIN))+
  geom_pointrange() +
  theme_classic()
```
Set criteria for minimal and aggressive exclusions

```{r}
if(exclusion.mode == 'AGGRESSIVE') {
  validation.threshold <- 50
}
if(exclusion.mode == 'MINIMAL') {
  validation.threshold <- 10
}

bad.subjects.validation <- validation.percent %>%
  filter(M <= validation.threshold) %>%
  pull(subject_id) %>%
  as.character()
```

## Final exclusion data

```{r}
bad.subjects <- unique(c(bad.subjects.prop.samples, bad.subjects.validation))

@@
